Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-08 paper.tex
additional paragraph to section 3.4

One may also notice that such a paradigm, {\it i.e.}, verification and synthesis based on an expected system behavior, is not restricted to digital filters and controllers or DMA races, but it can also be applied to possibly any real system, as long as the desired behavior can be expressed as properties in BMC frameworks. For instance, regarding self-driving cars, an important property could be the detection of pedestrians, animals, bicycles, or any obstacle present on urban and rural roads. Indeed, bicycles are considered one of the most difficult problems, due to the myriad of possible shape and colors \cite{selfcar}. In addition, the mentioned problem is closely related to machine learning, from which refinement strategies can be devised and incorporated to BMC approaches \cite{BMCml}.

>>>>

One may also notice that such a paradigm, {\it i.e.}, verification and synthesis based on an expected system behavior, is not restricted to digital filters and controllers or DMA races, but it can also be applied to possibly any real system, as long as the desired behavior can be expressed as properties in BMC frameworks. For instance, regarding self-driving cars, an important property could be the detection of pedestrians, animals, bicycles, or any obstacle present on urban and rural roads. Indeed, bicycles are considered one of the most difficult problems, due to the myriad of possible shape and colors \cite{selfcar}. In addition, the mentioned problem is closely related to machine learning, from which refinement strategies can be devised, incorporated to BMC approaches \cite{BMCml}, and directly applied to ECPS verification.

In summary, current approaches already tackle ECPS characteristics ({\it e.g.}, interaction with real world entities and digital processing), which are included in verification and synthesis methodologies. Finally, the final complement may come from ML techniques, which have the potential to fill gaps ({\it e.g.}, lack of complete models including nondeterminism), bridge tools and models ({\it e.g.}, analog and digital domains in ECPSs and verification schemes), and provide model and methodology evolution.
